Verifying Demonstrations

### 2018-11-21 paper/adversary-model.tex
Renames identity--cause -> identity--proof-share, removed location adv
Aligns formal adversary model with the rest

\subsection{Privacy adversary}%
\label{adversary-model-different-levels}

We provide one system model with two possible adversaries: one who tries to link a protester's real identity (\(P\)) to a protest proof-share (\(\cid\)) and one 
that aims at linking a protester's or a witness's real identity (\(P\), respectively \(W\)), to a location (\(l\)).
We also define varying strengths of each adversary.

\paragraph{The identity--proof share linking adversary}

There are three players: the protest participant (with identity) \(P\), a witness (with identity) \(W\) and the storage \(S\).
The adversary \(A\) controls \(W\) and \(S\).

\begin{definition}[Base identity--proof share adversary]%
  \label{base-identity-proof-share-adversary}
  The protester \(P\) and the witness \(W\) communicate.
  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
  \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly, only if those appear in the data \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
\end{definition}

This definition is illustrated in \cref{fig:identity-proof-share-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-identity-proof-share-adversary.tikz}
  \caption{\label{fig:identity-proof-share-adversary}%
    An overview of the base identity--proof share adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(\cid, P)\), 
    and the time it happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

We find \cref{base-identity-proof-share-adversary} suitable when the protester and witness both move in a crowd and there is no way for the witness to decide exactly with whom he or she communicates with.
However, in some situations this might not be the case, \eg the crowd is not dense.
In these situations the witness will likely see the face of the protester.
We capture this by the following definition.

\begin{definition}[Stronger identity--proof share adversary]%
  \label{stronger-identity-proof-share-adversary}
  The situation is the same as in \cref{base-identity-proof-share-adversary}, but now the 
  witness \(W\) learns the protester \(P\)'s identity.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.
\end{definition}

@@

\begin{definition}[Strongest identity--proof share adversary]%
  \label{strongest-identity-proof-share-adversary}
  Everything is the same as in \cref{stronger-identity-proof-share-adversary}, except that now \(S\) also learns \(P\)'s identity.
\end{definition}

>>>>

\subsection{Adversary model}%
\label{formal-adversary-model}

We now provide a concretely defined system and adversary model.
We give three definitions, each defines an adversary with increasingly stronger 
capabilities (\ie more auxiliary information).

There are three players: the protest participant (with identity) \(P\), a 
witness (with identity) \(W\) and the storage \(S\).
The adversary \(A\) controls \(W\) and \(S\).
This is illustrated in \cref{fig:base-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the base adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time it happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

\begin{definition}[Base adversary]%
  \label{base-adversary}
  The protester \(P\) and the witness \(W\) communicate.
  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when the 
  communication occurred \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly from the communication medium, only if those appear in the data 
    \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
\end{definition}

The base adversary (\cref{base-adversary}) represents an adversary that has no 
access to auxiliary information, \eg inferences that can be done from the 
communication layer, which means that it has only the protocol data at its 
disposal.

We find \cref{base-adversary} suitable when the protester and witness both move 
in a crowd and there is no way for the witness to decide exactly with whom he 
or she communicates with.
However, in some situations this might not be the case: \Eg if the crowd is not 
dense the witness will likely see the face of the protester.
If the witness is controlled by the adversary, then it is likely that the 
witness can capture a picture of the face, which can be turned into an identity 
through face recognition.
There are various such scenarios leading to the adversary learning the 
protester's identity, we capture this by the following definition.

\begin{definition}[Deanonymizing-witness adversary]%
  \label{deanonymizing-witness-adversary}
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.
\end{definition}

@@

\begin{definition}[Deanonymizing adversary]%
  \label{deanonymizing-adversary}
  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
\end{definition}
